### 2023-09-04 paper/sec-dis-pseudodata.tex
Mentioned fred=0.5 in xFitter results with stat+syst uncertainties, and that for EPPS21 we first obtain uncertainties at 90% CL and scale them down to 68% CL afterwards

 For this reason, following the HL-LHC projection strategy of~\cite{AbdulKhalek:2018rok},
 here we neglect bin-by-bin correlations
 and add in quadrature statistical and systematic errors,
 \be
\label{eq:covmat_definition_v2}
 {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
+ \delta_{ij}\lp f_{\rm corr}\rp^2\sum_{k=1}^{n_{\rm sys}} \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp^2
\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, .
\ee
In Eq.~(\ref{eq:covmat_definition_v2}) we have introduced a parameter $f_{\rm red}^{(k)}\le 1$
that gauges the impact of a possible reduction of the $k$-th systematic error
as compared to the default experiment performance (reproduced with $f_{\rm red}=1$).
%
Furthermore, $f_{\rm corr}$ represents an effective correction factor that accounts for the fact that data with correlated
systematics may be more constraining than the same data where each source of error is simply
added in quadrature as we do here.
%
A value of $f_{\rm corr} \sim 0.5$, obtained from the inspection of available measurements
 for which the full information
 on correlated systematics is available, was estimated in ~\cite{AbdulKhalek:2018rok}
 and we adopt the same choice here.
%
 In Sect.~\ref{sec:protonPDFs} we present results for the conservative scenario with
 $f_{\rm red}=1$, but it is
 straightforward to revisit the projections for a more optimistic
 detector performance with $f_{\rm red}< 1$.

@@

For ensure consistency, the PDF set and other theory settings, such as the perturbative
order and heavy quark scheme, adopted for the evaluation of
Eq.~(\ref{eq:theory_dis_projections}) should be the same as those
used in the fitting framework assessing their impact.
%
For instance, when using the {\sc\small xFitter} profiling of PDF4LHC21, one needs
 to generate  neutrino structure functions also using PDF4LHC21 as input.
 %
This ensures that the generated pseudo-data is coherent with the prior PDF
 set used as baseline and avoids introducing artificial inconsistencies 
 compromising the validity of the projection studies.

@@

The profiling studies carried out in this work are performed using version 2.2.1
of the 
{\sc\small xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}.
%
To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is made available in {\sc\small xFitter}.
%
All the experimental and theoretical data files used in the analysis, including
the  {\sc\small PineAPPL}  grids, are available
from the public {\sc\small xFitter} repository.
%
For the proton PDF profiling, a tolerance of $T^2 = 10$ is adopted,
which  corresponds approximately to the average tolerance
used in the CT18~\cite{Hou:2019efy} and MSHT20~\cite{Bailey:2020ooq} determinations,
the two Hessian sets entering the PDF4LHC21 combination~\cite{PDF4LHCWorkingGroup:2022cjn}, for
one-sigma PDF uncertainties.
%
For the Hessian profiling of EPPS21, a value of $T^2 = 20$ is used consistently with~\cite{Eskola:2021nhw}
for the definition of 68\%  confidence level intervals.

>>>>

 For this reason, following the HL-LHC projection strategy of~\cite{AbdulKhalek:2018rok},
 here we neglect bin-by-bin correlations
 and add in quadrature statistical and systematic errors,
 \be
\label{eq:covmat_definition_v2}
 {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
+ \delta_{ij}\lp f_{\rm corr}\rp^2\sum_{k=1}^{n_{\rm sys}} \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp^2
\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, .
\ee
In Eq.~(\ref{eq:covmat_definition_v2}) we have introduced a parameter $f_{\rm red}^{(k)}\le 1$
that gauges the impact of a possible reduction of the $k$-th systematic error
as compared to the default experiment performance (reproduced with $f_{\rm red}=1$).
%
Furthermore, $f_{\rm corr}$ represents an effective correction factor that accounts for the fact that data with correlated
systematics may be more constraining than the same data where each source of error is simply
added in quadrature as we do here.
%
A value of $f_{\rm corr} \sim 0.5$, obtained from the inspection of available measurements
 for which the full information
 on correlated systematics is available, was estimated in ~\cite{AbdulKhalek:2018rok}
 and we adopt the same choice here.
% 
In Sect.~\ref{sec:pdf4lhc21} and Sect.~\ref{sec:nuclearPDFs} we present results with $f_{\rm red}=0.5$, 
 while the remainder of Sect.~\ref{sec:protonPDFs} assumes the conservative scenario $f_{\rm red}=1$, 
 but it is straightforward to revisit the projections for a more optimistic detector performance with $f_{\rm red}< 1$.

@@

To ensure consistency, the PDF set and other theory settings, such as the perturbative
order and heavy quark scheme, adopted for the evaluation of
Eq.~(\ref{eq:theory_dis_projections}) should be the same as those
used in the fitting framework assessing their impact.
%
For instance, when using the {\sc\small xFitter} profiling of PDF4LHC21, one needs
 to generate  neutrino structure functions also using PDF4LHC21 as input.
 %
This ensures that the generated pseudo-data is coherent with the prior PDF
 set used as baseline and avoids introducing artificial inconsistencies 
 compromising the validity of the projection studies.

@@

The profiling studies carried out in this work are performed using version 2.2.1
of the 
{\sc\small xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}.
%
To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is made available in {\sc\small xFitter}.
%
All the experimental and theoretical data files used in the analysis, including
the  {\sc\small PineAPPL}  grids, are available
from the public {\sc\small xFitter} repository.
%
For the proton PDF profiling, a tolerance of $T^2 = 10$ is adopted,
which  corresponds approximately to the average tolerance
used in the CT18~\cite{Hou:2019efy} and MSHT20~\cite{Bailey:2020ooq} determinations,
the two Hessian sets entering the PDF4LHC21 combination~\cite{PDF4LHCWorkingGroup:2022cjn}, for
one-sigma PDF uncertainties.
%
For the Hessian profiling of EPPS21, a value of $T^2 = 33$ is used consistently with~\cite{Eskola:2021nhw}, and the resulting uncertainties are scaled down by a factor of 1.645 to obtain 68\% confidence level intervals.
